\LaTeX\ Author Guidelines for 3DIMPVT Proceedings

### 2012-06-15 3dimpvt/template/egpaper_final.tex
added michaels draft and new draft also

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

@@

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

@@

\author{First Author\\
  Institution1\\
  Institution1 address\\
  {\tt\small firstauthor@i1.org}
  % For a paper whose authors are all at the same institution, omit
  % the following lines up until the closing ``}''.  Additional
  % authors and addresses can be added with ``\and'', just like the
  % second author.  To save space, use either the email address or
  % home page, not both
  \and
  Second Author\\
  Institution2\\
  First line of institution2 address\\
  {\small\url{http://www.author.org/~second}} }

\maketitle
% \thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
  Automated 3D modeling of building interiors is used in applications
  such as virtual reality and environment mapping. Texture mapping
  these models accurately is vital towards visualizing the data
  gathered by modeling systems and increases overall usability. The
  localization of cameras in 3D scenes often suffers from
  inaccuracies, resulting in visible discontinuties when different
  images are projected onto a texture. Previous approaches at
  minimizing these discontinuities suffer from error accumulation when
  stitching together multiple images and do not robustly handle wide
  ranges of camera locations and angles. We propose two approaches for
  reducing discontinuities during texture mapping, tailored towards a
  backpack-mounted data acquisition system.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
Three-dimensional modeling of indoor environments has a variety of
applications such as training and simulation for disaster management,
virtual heritage conservation, and mapping of hazardous sites. Manual
construction of these digital models can be time consuming, and as
such, automated 3D site modeling has garnered much interest in recent
years.

The first step in automated 3d modeling is the physical scanning of
the environment's geometry. An indoor modeling system must be able to
calculate camera locations within an environment while simulatenously
reconstructing the 3D structure of the environment itself. This
problem is studied by the robotics and computer vision communities as
the simultaneous localization and mapping (SLAM) problem, and is
generally solved using a combination of laser range scanners, cameras,
and inertial measurement units (IMUs).

The aim of this paper is to present a solution for texture mapping the
3D models generated by indoor modeling systems, with specific
attention given to a human-operated system with higher localization
errors and greater variance in camera locations. The paper is
organized as follows. Section 2 provides an overview of the backpack
modeling system from which data and examples used throughout this
paper are from. Section 3 describes the general problem of 3D texture
mapping and reviews existing approaches. Section 4 describes
challenges posed by the backpack modeling system and presents our two
approaches tailored for walls and floors/ceilings
respectively. Section 5 compares results and presents conclusions.

\section{Backpack Modeling System}
Human-operated data acquisition systems provide unique advantages in terms of agility and portability over vehicular-mounted systems. Unfortunately, human-operated systems suffer from a lack of automation and stability, resulting in higher localization variance and leading to the problems discussed in Section 4.

\subsection{Data Acquisition Hardware}
The backpack modeling system from which our data was collected contains five 2D laser range scanners, two cameras, an orientation sensor, and an IMU (Should I even mention the IMU at all?). The laser scanners are 40Hz Hokuyo UTM-30LX 2D laser scanners with a 30-meter range and a 270$^{\circ}$ field of view. These scanners are mounted orthogonally to one another. The two cameras are Point Grey Grasshopper GRAS-50S5C units equipped with fisheye lenses, resulting in a 180$^{\circ}$ field of view. The IMU, a Honeywell HG9900, is a strap-down navigation-grade sensor which combines three ring laser gyros with bias stability of less than 0.003$^{\circ}$/hour and three precision accelerometers with bias of less than 0.245mm/sec$^{2}$. The HG9900 provides highly accurate measurements of all 6 DOF at 200Hz and thus serves as our ground truth for the experiments in this paper. ]The orientation sensor (OS), an InterSense InertiaCube3, provides orientation parameters at a rate of 180Hz.

\subsection{Environment Reconstruction}
Using a combination of these sensors and multiple localization and loop-closure algorithms, the backpack is localized over its data collection period, and a 3D point cloud of our environment is constructed. Approximate normal vectors for each point in the point cloud are then calculated by gathering neighboring points within a small radius and running a Principal Component Analysis procedure. These normal vectors allow for the classification and grouping of adjacent points into structures such as walls, ceilings, floors, and staircases. A RANSAC algorithm is then employed to fit polygonal planes to these structured groupings of points, resulting in a fully planar model. This planar model, consisting of multiple 2D polygonal planes in 3D space, along with the set of images captured by the backpack's camera, can be considered the input data on which our approach runs.

\subsection{Image Subsampling}
Before beginning the texture mapping process, it is prudent to reduce the amount of potential images being considered for texture mapping each plane. The backpack modeling system takes 5 pictures/second from both cameras, resulting in each plane being present in (and capable of being textured mapped by) thousands of images, at a wide variance of distances and angles. Thus, for the sake of efficiency, it makes sense to associate each plane with a much smaller sample of images. When creating this subset of images for each plane, there are three criteria we keep in mind. First, we want such a subset of images to be capable of texturing the entirety of a plane, so as to ensure there are no holes in our final texture. Second, we want all our images to be taken from a relatively close distance to the plane, and at as much of a direct, head-on angle as possible. This ensures that the image projects squarely onto our desired plane, with minimal inclusion of other planes, and we get a texture with high resolution. Third, we desire an amount of overlap between the images chosen. This overlap helps us with preprocessing as well as postprocessing techniques discussed in Sections x and y.

To meet these three criteria, we tesselate each plane into [X] triangles of [Y] size. For each triangle, we find all images that can be projected upon the entirety of the triangle, accounting for occlusion with other planes as well, using standard ray-polygon intersection tests. Of these images, we then select the best one according to the heuristic in equation X, favoring closer distances and more head-on viewing angles. We also enforce that no two images are chosen such that they were taken within 0.5 meters of eachother. This results in a greatly-reduced set of images such that each one is objectively the "best" location-wise for some number of areas on the plane, addressing the first two criteria. Furthermore, since cameras are only at good angles to triangles near their center of projection, images will be chosen such that there is high overlap between them. This process reduces the amount of candidate images for each plane from many thousands to around 50, at fairly even spacing. With this completed, each of our planes is associated with a sufficiently sized list of candidate images, and we are ready to begin texture mapping.

\section{NOTES}
4 Special Considerations due to BMS blabla sucky title
The backpack modeling system described in Section 2 was designed to prioritize for texturing walls. As mentioned previously, the backpack contains two fisheye cameras, one aimed directly to the left of the backpack operator, and one aimed directly to the right. Thus, in order to texture the ceiling where the operator walked, images from both cameras must be combined. Even more problematic, the floor beneath the backpack is physically obscured by the operator's body, and thus must be textured by images taken from different locations. These problems are compounded by the fact that the operator's data acquisition path attempts to fully scan each wall, but not necessarily the entirety of a floor or ceiling. This means that large swaths of floors and ceilings are never walked directly over or under, and thus must be textured by sidelong images taken from further distances and at oblique angles. We strongly prefer head-on images because when images are projected onto a planar surface at an extreme angle, the resultant texture ends up spanning a large portion of the plane, applying low-resolution textures to areas at a great distance from the camera location.

In short, these factors mean that wall planes are associated with a multitude of upright, uniform images, taken head-on and from a relatively close distance at regular intervals, while floors and ceilings are associated with images of all orientations and distances. This major difference suggests we employ two strategies, one tailored for each scenario.

4.1 Texturing Floors and Ceilings

4.2 Texturing Walls
Since our candidate images for texturing a wall are all taken from similar distances and orientations relative to our wall, their individual "qualities" are all fairly similar. We don't have to worry as much about filtering out bad images; rather we seek to select some subset of our images which together form a good texture.

5 Results and Analysis
but also occlusion projection thing. door projected onto wall is fine, door projected onto floor is bad.

\section{EVERYTHING AFTER HERE IS TEMPLATE STUFF}

\section{Introduction}

@@

% -------------------------------------------------------------------------
\subsection{Language}

@@

By submitting a manuscript to 3DIMPVT, the authors assert that it has
not been previously published in substantially similar
form. Furthermore, no paper which contains significant overlap with
the contributions of this paper either has been or will be submitted
during the 3DIMPVT 2012 review period to {\bf either a journal} or any
conference or any workshop.  {\bf Papers violating this condition will
  be rejected}.

@@

% -------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in
the version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the
ruler should not change the appearance of any other content on the
page.  The camera ready copy should not contain a ruler. (\LaTeX\
users may uncomment the \verb'\cvprfinalcopy' command in the document
preamble.)  Reviewers: note that the ruler measurements do not align
well with lines in the paper --- this turns out to be very difficult
to do well when the paper contains many figures and equations, and,
when done, looks ugly.  Just use fractional references (e.g.\ this
line is $097.15$), although in most cases one would expect that the
approximate location will be adequate.

@@

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.
Just because you didn't refer to it in the text doesn't mean some
future reader might not need to refer to it.  It is cumbersome to have
to use circumlocutions like ``the equation second from the top of page
3 column 1''.  (Note that the ruler will not be present in the final
copy, so is not an alternative to equation numbers).  All authors will
benefit from reading Mermin's description of how to write mathematics:
\url{http://www.cvpr.org/doc/mermin.pdf}.

@@

Sometimes your paper is about a problem which you tested using a tool
which is widely known to be restricted to a single institution.  For
example, let's say it's 1969, you have solved a key problem on the
Apollo lander, and you believe that the CVPR70 audience would like to
hear about your solution.  The work is a development of your
celebrated 1968 paper entitled ``Zero-g frobnication: How being the
only people in the world with access to the Apollo lander source code
makes us a wow at parties'', by Zeus \etal.

@@

\begin{figure}[t]
  \begin{center}
    \fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
    % \includegraphics[width=0.8\linewidth]{egfigure.eps}
  \end{center}
  \caption{Example of caption.  It is set in Roman so that mathematics
    (always set in Roman: $B \sin A = A \sin B$) may be included
    without an ugly clash.}
  \label{fig:long}
  \label{fig:onecol}
\end{figure}

@@

% ------------------------------------------------------------------------
\section{Formatting your paper}

@@

% -------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must
be kept within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8
inches (22.54 cm) high.

% -------------------------------------------------------------------------
\subsection{Type-style and fonts}

@@

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

@@

% -------------------------------------------------------------------------
\subsection{Footnotes}

@@

% -------------------------------------------------------------------------
\subsection{References}

@@

% -------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

@@

% -------------------------------------------------------------------------
\subsection{Color}

@@

% ------------------------------------------------------------------------
\section{Final copy}

@@

% Please direct any questions to the production editor in charge of
% these proceedings at the IEEE Computer Society Press: Phone (714)
% 821-8380, or Fax (714) 761-1784.

>>>>

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
%\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

@@

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

@@

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous 3DIMPVT/3DIM/3DPVT abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

@@

%-------------------------------------------------------------------------
\subsection{Language}

@@

By submitting a manuscript to 3DIMPVT, the authors assert that it has not been
previously published in substantially similar form. Furthermore, no paper
which contains significant overlap with the contributions of this paper
either has been or will be submitted during the 3DIMPVT 2012 review period to
{\bf either a journal} or any conference or any
workshop.
 {\bf Papers violating this condition will be rejected and a list of violating authors may be included in the proceedings.}

@@

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

@@

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics.%: \url{http://www.cvpr.org/doc/mermin.pdf}.

@@

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the 3DIMPVT12 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

@@

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

@@

%------------------------------------------------------------------------
\section{Formatting your paper}

@@

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.  Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this fine the line (around
line 23)  
\begin{verbatim}
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 46
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

@@

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before.

@@

%-------------------------------------------------------------------------
\subsection{Footnotes}

@@

%-------------------------------------------------------------------------
\subsection{References}

@@

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

@@

%-------------------------------------------------------------------------
\subsection{Color}

@@

%------------------------------------------------------------------------
\section{Final copy}

@@
